RIScatter: Unifying Backscatter Communications and Reconfigurable Intelligent Surface From a Probabilistic Perspective

### 2022-11-02 main.tex
:pencil: Input distribution vs weights

% \title{RIScatter: Unifying Backscatter Communications and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
\title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}

@@

		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
		% ! SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
		Fig. \ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those applications.
		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when $N$ is sufficiently large.
		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
		Such an \gls{sr} requires a sufficiently large $N$ to guarantee the primary performance, but decreases the backscatter symbol rate by a factor of $N$ and requires $N$ \gls{sic} processes to decode each backscatter symbol (tuple).
		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, but the multipath benefit of \gls{sr} is unobvious.
		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
		\gls{ris} always ensures constructive superposition of direct and scattered components, but \gls{sr} only creates a quasi-static rich-scattering environment that stochastically enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff by smart input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern (no need for backscatter detection) when the primary link is prioritized.
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
		This is because both RIScatter and \gls{ambc} employ semi-coherent (instead of coherent) energy detection in the presence of primary uncertainty, and RIScatter with adaptive channel coding achieves higher backscatter rate than \gls{ambc} with equiprobable inputs.
		Importantly, such a semi-coherent backscatter detection is feasible for arbitrary $N$, and using a fast-switching node with small $N$ can increase the backscatter throughput per unit time and preserve the dynamic passive beamforming gain.
		% It only requires one energy comparison, re-encoding, and precoding operations to decode each backscatter symbol (tuple).
	\end{subsection}

	\begin{subsection}{Input Distribution under Different Weights}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/distribution_weights.tex}
			}
			\caption{Typical reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$ and $N=20$.}
			\label{fg:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate each RIScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights in Fig. \ref{fg:distribution_weights}.
		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
		gradually progresses from slightly skewed to completely biased.
		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
		In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
		Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
	\end{subsection}

>>>>

\title{RIScatter: Unifying Backscatter Communications and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
% \title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}

@@

		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
		% ! SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
		Fig. \ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those applications.
		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when $N$ is sufficiently large.
		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
		Such an \gls{sr} requires a sufficiently large $N$ to guarantee the primary performance, but decreases the backscatter symbol rate by a factor of $N$ and requires $N$ \gls{sic} processes to decode each backscatter symbol (tuple).
		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, but the multipath benefit of \gls{sr} is unobvious.
		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
		\gls{ris} always ensures constructive superposition of direct and scattered components, but \gls{sr} only creates a quasi-static rich-scattering environment that stochastically enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff by smart input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by deterministic reflection pattern (no need for backscatter detection).
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
		This is because both RIScatter and \gls{ambc} employ semi-coherent (instead of coherent) energy detection in the presence of primary uncertainty, and RIScatter with adaptive channel coding achieves higher backscatter rate than \gls{ambc} with equiprobable inputs.
		Importantly, such a practical RIScatter detection is feasible for arbitrary $N$, and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
	\end{subsection}

	\begin{subsection}{Input Distribution under Different Weights}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/distribution_weights.tex}
			}
			\caption{Typical RIScatter reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$ and $N=20$.}
			\label{fg:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate RIScatter nodes can leverage \gls{csi}- and weight-adaptive input distribution design to balance backscatter modulation and passive beamforming.
		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is also global optimal in this example.} under different weights and present the result in Fig. \ref{fg:distribution_weights}.
		At $\rho=0$ where backscatter performance is prioritized, the optimal input distribution is zero on two states and nearly uniform on the other two.
		This is because, due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as illustrated in Fig. \ref{fg:energy_distribution}.
		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the others may not provide enough energy difference and end up unused.
		At $\rho=1$ where primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, which demonstrates RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.

		% gradually progresses from slightly skewed to completely biased.
		% For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
		% On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
		% In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
		% Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
		% For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
	\end{subsection}
